---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```

# possibilitylabthemes

<!-- badges: start -->
<!-- badges: end -->

possibilitylabthemes provides a custom ggplot2 theme with Possibility Lab color palettes and styles. 

## Installation

possibilitylabthemes is still in development, but you can 
install the development version of possibilitylabthemes from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Possibility-Lab/possibilitylabthemes")
```

## Using the theme

You can set the Possibility Lab theme as the default for an R session. 

```{r defaults, message=FALSE, warning=FALSE}
library(tidyverse)
library(extrafont)
extrafont::loadfonts(device = "win")

library(possibilitylabthemes)
possibility_defaults()
```

```{r eu_df, include=FALSE}
dv <- lubridate::date_decimal(time(EuStockMarkets)[1:nrow(EuStockMarkets)])

df <- datasets::EuStockMarkets %>%
  as.data.frame() %>%
  mutate(time = dv) %>% 
  pivot_longer(DAX:FTSE,
               names_to = "index",
               values_to = "price")
```


```{r eu_stocks}
ggplot(df) +
  geom_line(aes(time, price, color = index)) +
  labs(title = "Daily Closing Prices of Major European Stock Indices, 1991-1998")
```


To use color palettes other than the default, you can use 
`scale_color_manual(values = possibility_palette("discrete"))`, for example. 
Palettes available can be returned by `possibility_palettes`. 

When you wish to add more major or minor gridlines, use `possibility_add_grid()`.

```{r orange}
ggplot(datasets::Orange) +
  geom_line(aes(age, circumference, color = Tree), alpha = 0.8) +
  geom_point(aes(age, circumference, color = Tree)) +
  
  scale_color_manual(values = possibility_palette("discrete")) +
  
  possibility_add_grid(add_minor = "both") +
  
  labs(title = "Orange Tree Growth",
       subtitle = "from the datasets package")
```

```{r starwars}
ggplot(filter(starwars, species %in% c("Human", "Droid", "Wookiee") &
                !is.na(height))) +
  geom_point(aes(height, reorder(name, height), color = species)) +
  scale_color_manual(values = possibility_palette("secondary")) +
  labs(title = "Heights of various Star Wars characters")
```

## Maps
You can set the default theme to a "map" style.

```{r berkeley_map, message=F, warning=F, echo=T}
possibility_defaults("map")

berk <- sf::st_read(
  "https://data.cityofberkeley.info/api/geospatial/6is2-y2ia?method=export&format=GeoJSON")

blvds <- sf::st_read(
  "https://data.cityofberkeley.info/api/geospatial/fgw9-98ic?method=export&format=GeoJSON") %>% 
  mutate(type = "Bicycle Boulevard") %>% 
  select(type, geometry)

trails <- sf::st_read(
  "https://data.cityofberkeley.info/api/geospatial/yepa-z7vf?accessType=DOWNLOAD&method=export&format=GeoJSON"
  ) %>% 
  mutate(type = "Path") %>% 
  select(type, geometry)

streets <- sf::st_read(
  "https://data.cityofberkeley.info/api/geospatial/hqnk-qfhq?method=export&format=GeoJSON")

paths <- streets %>% filter(street_typ %in% c("PATH", "TRAIL")) %>% 
  mutate(type = "Path") %>% 
  select(type, geometry)

routes <- rbind(blvds, trails, paths)


ggplot(data = sf::st_intersection(
         filter(streets, !(street_typ %in% c("PATH", "TRAIL"))),
         berk)
       ) +
  geom_sf(color = "#d6d6d6") +
  geom_sf(data = routes, aes(color = type)) +
  labs(title = "Getting around Berkeley on named paths and bicycle boulevards")

```



## Saving plots

Use `possibility_save()` to save plots as png files. Preset sizes - "small", "medium", 
or "large" - will save your plot at predetermined dimensions and scale all fonts and graphic
elements accordingly. Choose an orientation - "horizontal" or "vertical" - depending 
on your chart type. `possibility_save()` uses `ragg::agg_png` to save as a png file, 
which is the most suitable file format for including graphics in word documents and 
presentations.

```{r save, eval=FALSE}

possibility_save("save_destination_filepath.png",
                 x = ggplot2::last_plot(),
                 preset_size = "medium",
                 orientation = "vertical",  ## default is "horizontal"
                 dpi = 300) 

```


## Font: Source Sans Pro
Possibility Lab uses the Source Sans Pro font. Help with installing and 
testing fonts will be added soon. 

## Citations
Thanks and credit to the [urbnthemes](https://github.com/UrbanInstitute/urbnthemes) package for inspiration and examples. 
