---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```

# possibilitylabthemes

<!-- badges: start -->
<!-- badges: end -->

possibilitylabthemes provides a custom ggplot2 theme with Possibility Lab color palettes and styles. 

## Installation

You can install the development version of possibilitylabthemes from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Possibility-Lab/possibilitylabthemes")
```

## Using the theme

You can set the Possibility Lab theme as the default for an R session. 

```{r example, echo=FALSE, }
library(tidyverse)
library(possibilitylabthemes)

possibility_defaults()
```

You can specify certain visualization types for more a more tailored theme.

```{r cars, echo=F}
possibility_defaults("map")
```


Set the Possibility Lab theme as the default, then plot with ggplot as normal. 
To use color palettes other than the default, you can use 
`scale_color_manual(values = possibility_palette("discrete"))`, for example. 
Palettes available can be returned by `possibility_palettes`.

```{r pressure, echo = FALSE}
possibility_defaults()

ggplot(datasets::Orange) +
  geom_line(aes(age, circumference, color = Tree), alpha = 0.8) +
  geom_point(aes(age, circumference, color = Tree)) +
  
  scale_color_manual(values = possibility_palette("discrete")) +
  
  possibility_add_grid(add_minor = "both") +
  
  labs(title = "Orange Tree Growth",
       subtitle = "from the datasets package")
```

## Font
Possibility Lab uses the Source Sans Pro font. Help with installing and 
testing fonts will be added soon. 

## Citations
Thanks to the [urbnthemes](https://github.com/UrbanInstitute/urbnthemes) package for inspiration and examples. 
